---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# biorrxiv

R client for interacting with the [bioRxiv API](https://api.biorxiv.org)

** This is a (very incomplete) work in progress **

## Installation

Install the development version from Github:

```{r eval=FALSE}

install.packages("devtools")
devtools::install_github("nicholasmfraser/biorrxiv")

```

## Usage

The main functions in `biorrxiv` loosely conform to the API endpoints outlined in the API documentation ([see here](https://api.biorxiv.org/)).

### Content detail

Retrieve details of either a set of preprints deposited between two dates, or lookup a single preprint by DOI:

```{r eval=FALSE}

# Get details of preprints deposited between 2018-01-01 and 2018-01-10
# By default, only the first 100 records are returned
biorrxiv_content(from = "2018-01-01", to = "2018-01-10")

# Set a limit to return more than 100 records
biorrxiv_content(from = "2018-01-01", to = "2018-01-10", limit = 200)

# Or set limit as "*" to return all records
biorrxiv_content(from = "2018-01-01", to = "2018-01-10", limit = "*")

# Skip the first 100 records
biorrxiv_content(from = "2018-01-01", to = "2018-01-10", limit = 200, skip = 100)

# By default, data is returned in a list. Use the "format" argument to specify
# that data should be returned in "json" format or as a data frame ("df").
biorrxiv_content(from = "2018-01-01", to = "2018-01-10", format = "df")

# Lookup a preprint by DOI
biorrxiv_content(doi = "10.1101/833400")

```

### Published article detail

Retrieve details of published articles associated with bioRxiv preprints that were published between two dates:

```{r eval=FALSE}

# Get details of all articles published between 2018-01-01 and 2018-01-10
biorrxiv_published(from = "2018-01-01", to = "2018-01-10", limit = "*", format = "df")

```

### Publisher article detail

Retrieve details of articles published by a specific publisher (specified by their doi prefix) between two dates:

```{r eval=FALSE}

# Get details of all articles published by eLife (prefix = 10.7554) between 2018-01-01 and 2018-01-10
biorrxiv_publisher(prefix = "10.7554", from = "2018-01-01", to = "2018-01-10", 
                   limit = "*", format = "df")

```

### Content summary statistics

Retrieve summary statistics for bioRxiv content (e.g. number of preprints deposited):
 
```{r eval=FALSE}

# Get summary statistics at a montly level
biorrxiv_summary(interval = "m")

# Get summary statistics at a yearly level
biorrxiv_summary(interval = "y")

```
 
### Usage summary statistics

Retrieve summary statistics for usage of bioRxiv content (e.g. number of pdf downloads):

```{r eval=FALSE}

# Get usage statistics at a montly level
biorrxiv_usage(interval = "m")

```

## Contributing

Contributors are extremely welcome! Please contribute here directly, or contact me at nicholasmfraser@gmail.com for more information.











