---
title: "rbiorxiv"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rbiorxiv}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## About bioRxiv and medRxiv

[bioRxiv](https://www.biorxiv.org/) and [medRxiv](https://www.medrxiv.org/) are a preprint repositoris for the biological and medical sciences, respectively, both hosted by the [Cold Spring Harbor Laboratory](https://www.cshl.edu/) (CSHL).

Metadata of preprints from both repositories can be accessed via a singular API service hosted on bioRxiv, available at [https://api.biorxiv.org](https://api.biorxiv.org/). This package, `rbiorxiv`, provides a simple interface for interacting with this API service, to allow retrieval of metadata for bioRxiv and medRxiv preprints.

## Installation

Install development version from Github

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("nicholasmfraser/rbiorxiv")
```

Load package

```{r eval=FALSE}
library(rbiorxiv)
```

## Usage

The main functions in `rbiorxiv` generally conform to the API endpoints outlined in the API documentation ([see here](https://api.biorxiv.org/)).

### Content detail

Retrieve details of either a set of preprints deposited between two dates, or lookup a single preprint by DOI:

```{r eval=FALSE}
# Get details of preprints deposited between 2018-01-01 and 2018-01-10
# By default, only the first 100 records are returned
biorxiv_content(from = "2018-01-01", to = "2018-01-10")

# Set a limit to return more than 100 records
biorxiv_content(from = "2018-01-01", to = "2018-01-10", limit = 200)

# Or set limit as "*" to return all records
biorxiv_content(from = "2018-01-01", to = "2018-01-10", limit = "*")

# Skip the first 100 records
biorxiv_content(from = "2018-01-01", to = "2018-01-10", limit = 200, skip = 100)

# By default, data is returned in a list. Use the "format" argument to specify
# that data should be returned in "json" format or as a data frame ("df").
biorxiv_content(from = "2018-01-01", to = "2018-01-10", format = "df")

# Lookup a preprint by DOI
biorxiv_content(doi = "10.1101/833400")
```

The bioRxiv API currently also allows querying of details of medRxiv preprints, by supplying a "server" parameter. This can be specified as follows:

```{r eval=FALSE}
# Get details of medRxiv preprints deposited between 2020-01-01 and 2020-01-02
biorxiv_content(server = "medrxiv", from = "2020-01-01", to = "2020-01-02")
```

The default server parameter is always "biorxiv". Note that the following functions documented below are limited to bioRxiv only (at the time of writing).

### Published article detail

Retrieve details of published articles associated with bioRxiv preprints that were published between two dates:

```{r eval=FALSE}
# Get details of all articles published between 2018-01-01 and 2018-01-10
biorxiv_published(from = "2018-01-01", to = "2018-01-10", limit = "*", format = "df")
```

### Publisher article detail

Retrieve details of articles published by a specific publisher (specified by their doi prefix) between two dates:

```{r eval=FALSE}
# Get details of all articles published by eLife (prefix = 10.7554) between 2018-01-01 and 2018-01-10
biorxiv_publisher(prefix = "10.7554", from = "2018-01-01", to = "2018-01-10", 
                   limit = "*", format = "df")
```

### Content summary statistics

Retrieve summary statistics for bioRxiv content (e.g. number of preprints deposited):
 
```{r eval=FALSE}
# Get summary statistics at a montly level
biorxiv_summary(interval = "m")

# Get summary statistics at a yearly level
biorxiv_summary(interval = "y")
```
 
### Usage summary statistics

Retrieve summary statistics for usage of bioRxiv content (e.g. number of pdf downloads):

```{r eval=FALSE}
# Get usage statistics at a montly level
biorxiv_usage(interval = "m")

# Get usage statistics at a yearly level
biorxiv_usage(interval = "y")
```
